introduction to signal and system

### 2019-11-26 Journal/20191118.tex
add the section of definition of signals and systems
also, the examples sections are added

% Intended LaTeX compiler: xelatex
\documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
\author{Eason}
\date{\today}
\title{20191119}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={20191119},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

\section{Tuesday, 11/19/19}
\label{sec:orgaf7c73e}
\subsection{21:55 this is a new week}
\label{sec:org784f7a1}
STEAM: science, technology, engineering, art and math

Today, I listen to an talk between 3blue1brown and numberphile.

\section{Wednesday, 11/20/19}
\label{sec:org7da6c22}

\section{Sunday, 11/24/19}
\label{sec:org9fb7c83}
\subsection{introduction to signal and system}
\label{sec:org4132682}
\subsubsection{preface}
\label{sec:org30a21fe}

@@

\subsubsection{15:39 Basics of signals and systems}
\label{sec:orgf198687}

@@

\subsubsection{definition of signals and systems}
\label{sec:org9f44052}

@@

A discrete-time signal is a sequence of values of interest, where the integer
index can be thought of as a time index, and the values in the sequence
represent some physical quantity of interest. Because many discrete-time signals
arise as equally-spaced samples of a continuous-time signal, it is often more
convenient to think of the index as the "sample number".

Systems process signals to produce a modified or transformed version of the
original signal. For the information and communication technology, signals and
systems helps engineer to analyze and design the signals and systems they meet
in daily life.

\subsubsection{summary of chapter 1}
\label{sec:orgde426c3}

@@

\subsubsection{references}
\label{sec:orgbf8c476}

@@

\item Dr Wickert's website \href{http://www.eas.uccs.edu/\~mwickert/}{Dr. Wickert's Info Center}  has quite a lot resources
for a engineering student.
\end{enumerate}
\end{document}

>>>>

% Intended LaTeX compiler: xelatex
\documentclass[koma,utopia,letterpaper,captions=tableheading,11pt,listings-sv,microtype,paralist,colorlinks=true,urlcolor=blue]{org-article}
\author{Eason}
\date{\today}
\title{introduction to signal and system}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={introduction to signal and system},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

\section{preface}
\label{sec:orgb73e917}

@@

\section{15:39 Basics of signals and systems}
\label{sec:org023432e}

@@

\section{definition of signals and systems}
\label{sec:org0083078}

Fist give the definition of singal then system.
\subsection{definition of signals}
\label{sec:orgc5b8c56}

@@

A discrete-time signal is a sequence of values of interest, where the integer
index can be thought of as a time index, and the values in the sequence
represent some physical quantity of interest. Because many discrete-time signals
arise as equally-spaced samples of a continuous-time signal, it is often more
convenient to think of the index as the "sample number".
\subsection{examples of signals}
\label{sec:org9e7ff00}

\subsubsection{ECG signal}
\label{sec:org6aa518f}

\subsubsection{Speech signal}
\label{sec:org4599249}

\subsubsection{Image}
\label{sec:orgb9ba77a}

\subsection{definition of systems}
\label{sec:org50a98a3}

Systems process signals to produce a modified or transformed version of the
original signal. For the information and communication technology, this series
of videos and posts help engineers analyze and design the signals and systems
they meet in daily life.

In general, two types of tools related with continuous-time signals and
discrete-time signals will be covered. For example, for the continuous-time
signals we have Fourier Transform and Laplace transform whereas for the
discrete-time signals we have discrete time Fourier Transforms and Z-transform.
Living in a digitized world, I use discrete-time signals related tools more
often than the continuous-time counterpart. Now, it seems that the
continuous-time signals only exists before analog-digital converter (ADC).
However, to analyze a signal, the continuous-time related tools provide a more
mathematical and theoretical way. So during the learning and teaching signals
and systems, I will cover both continuous-time and discrete-time topics and give
as many details about both realms as I can. Fortunately, we have sampling theory
and ADC, we can easily move from continuous-time world to discrete-time world .
Most of the conclusions we draw from the continuous-time world will apply in the
discrete-time world with no or only a little modification.
\subsection{examples of systems}
\label{sec:org371aacc}

\subsubsection{ECG system}
\label{sec:orge20180e}

\subsubsection{Voice recording system}
\label{sec:org4bc4f48}

\subsubsection{Camera Systems}
\label{sec:org36b0296}

\section{summary of chapter 1}
\label{sec:org273cc92}

@@

\section{references}
\label{sec:orgc602a8b}

@@

\item Dr Wickert's website \href{http://www.eas.uccs.edu/\~mwickert/}{Dr. Wickert's Info Center}  has quite a lot resources
for a engineering student.
\end{enumerate}
\section{architecture of each video}
\label{sec:org64de00f}

\begin{enumerate}
\item every video will contain several topics but the mathematical derivation will
not be so all-inclusive. More details will given as posts in this site for whom
may be interested. So you can grab the overall structure at first then
reinforce the it with more bricks.
\item For each video, only several key points will be explained. I don't want the
video make you feel boring or tired.
\item A piece of suggestion for the serious learner: watch the video twice or even
more. Most often, even some concepts which are relatively simple at first
look hide some deep relation with other concepts. The obscure relation will
not be illustrated in the video if it does not affect the understanding of
current object.
\end{enumerate}
\end{document}
